---
title: "Relationship between Exercise Addiction Risk and Social Interaction is Moderated by Depression and Eating Disorder"
author: "Chia-Chuan Yu, Ph.D."
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This is the 1st study in my dissertation, supervised by Darla Castelli, Ph.D. We investigated the associations between exercise addiction (EA) and three domains of social interaction (i.e., social support[ss], perceived discrimination[dis], fear of missing out [FoMO], and the importance of social reward[sr]) among young adults in Austin, TX. Furthermore, we examined whther these relationships are moderated by the symptoms of depression and eating disorder, which are the two common comorbidities of EA.

```{r include=FALSE}
library(readxl)
library(writexl)
library(dplyr)
library(mice)
library(MVN)
library(psych)
library(tableone)
library(ggcorrplot2)
library(ggplot2)
library(jtools)
library(interactions)
library(patchwork)
library(effects)
library(emmeans)
library(ppcor)
```

# Data imputation
This step is skipped because I've already done the imputation, which took a long time to run.
```{r}
# df <- read_excel(path = "/Users/chia-chuanyu/Desktop/dissertationData/study1/study1_organizedFinal.xlsx",
#                  sheet = "organized_forImputation")
# column_names <- c('eai1', 'eai2', 'eai3', 'eai4', 'eai5', 'eai6',
#               'idea81', 'idea82', 'idea83', 'idea84', 'idea85', 'idea86', 'idea87', 'idea88',
#               'ipaqsf_vigMET', 'ipaqsf_modMET', 'ipaqsf_walkMET', 'ipaqsf_sit',
#               'edeqs1', 'edeqs2', 'edeqs3', 'edeqs4', 'edeqs5', 'edeqs6', 'edeqs7', 'edeqs8', 'edeqs9', 'edeqs10', 'edeqs11', 'edeqs12',
#               'phq1', 'phq2', 'phq3', 'phq4', 'phq5', 'phq6', 'phq7', 'phq8', 'phq10',
#               'mosss1', 'mosss2', 'mosss3', 'mosss4', 'mosss5', 'mosss6', 'mosss7', 'mosss8', 'mosss9', 'mosss10', 'mosss11', 'mosss12',
#               'mosss13', 'mosss14', 'mosss15', 'mosss16', 'mosss17', 'mosss18', 'mosss19',
#               'srq1', 'srq2', 'srq3', 'srq4', 'srq5', 'srq6', 'srq7', 'srq8', 'srq9', 'srq10', 'srq11', 'srq12', 'srq13', 'srq14', 'srq15',
#               'srq16', 'srq17', 'srq18', 'srq19', 'srq20', 'srq21', 'srq22', 'srq23',
#               'fomos1', 'fomos2', 'fomos3', 'fomos4', 'fomos5', 'fomos6', 'fomos7', 'fomos8', 'fomos9', 'fomos10',
#               'everyDiscrimiS1a','everyDiscrimiS2a', 'everyDiscrimiS3a', 'everyDiscrimiS4a', 'everyDiscrimiS5a')
# # Only include the specified columns and replaced 999 with NA
# df <- df[, column_names]
# df[df == 999] <- NA
# 
# # Define the imputation methods for each variable
# imp_methods <- make.method(df)
# # Predictive mean matching (pmm) method for continuous variables 
# imp_methods[column_names] <- "pmm"
# 
# # Imputation
# imp_data <- mice(df, m = 5, maxit = 50, method = imp_methods, seed = 500)
# completed_data <- complete(imp_data)
# write_xlsx(completed_data, path = "/Users/chia-chuanyu/Library/Mobile Documents/com~apple~CloudDocs/Chuan's Macbook Pro/My Ph.D/UT Austin/Research/Dissertation/publications/study1_onlineSurvey/final_imputed.xlsx")
# head(completed_data)
```

# Multivariate normality and outlier detection
Data violated multivariate normality assumption, thus in hypothesis testing we used log transformation after removing outliers.
```{r}
# Test multivariate normality
data <- read_excel("/Users/chia-chuanyu/Desktop/dissertationData/study1/study1_organizedFinal.xlsx", sheet = "finalForAnalyze")
# vars <- c('eai', 'edeqs', 'phq_9', 'mossss_overallSupportIndex', 'srq', 'fomos', 'everyDiscrimiS')
vars <- c('sex', 'eai', 'edeqs', 'phq_9', 'ipaqsf_totalMET', 'mossss_overallSupportIndex', 'srq', 'fomos', 'everyDiscrimiS')
data <- data[vars]
data_mn1 <- mvn(data, mvn_test = "mardia", scale = TRUE, descriptives = TRUE, bootstrap = TRUE, B = 10000)
summary(data_mn1)

# Outliers detection with Mahalanobis distance before log transformation
distances <- mahalanobis(data, colMeans(data), cov(data))
threshold <- qchisq(0.99, df = ncol(data))  # 99% CI (i.e., only remove extreme individuals)
outliers <- which(distances > threshold)
print(outliers)
print(length(outliers))
data_no_outliers <- data[-outliers, ]

# Test multivariate normality again
data_mn2 <- mvn(data_no_outliers, mvn_test = "mardia", scale = TRUE, descriptives = TRUE, bootstrap = TRUE, B = 10000)
summary(data_mn2)

# Print variables with 0 values, which are added by 1 in log transformation
colSums(data_no_outliers[, vars] == 0, na.rm = TRUE) > 0

# Check multivariate normality after log transformation, just check.
data_clean <- data_no_outliers %>%
  mutate(
    eai  = log(eai),
    edeqs = log(edeqs + 1),
    phq_9 = log(phq_9 + 1),
    ipaqsf_totalMET = log(ipaqsf_totalMET + 1),
    mossss_overallSupportIndex = log(mossss_overallSupportIndex),
    srq  = log(srq),
    fomos = log(fomos),
    everyDiscrimiS = log(everyDiscrimiS + 1)
  )

data_clean$eai <- scale(data_clean$eai)
data_clean$edeqs <- scale(data_clean$edeqs)
data_clean$phq_9 <- scale(data_clean$phq_9)
data_clean$ipaqsf_totalMET <- scale(data_clean$ipaqsf_totalMET)
data_clean$mossss_overallSupportIndex <- scale(data_clean$mossss_overallSupportIndex)
data_clean$srq <- scale(data_clean$srq)
data_clean$fomos <- scale(data_clean$fomos)
data_clean$everyDiscrimiS <- scale(data_clean$everyDiscrimiS)

data_mn3 <- mvn(data_clean, mvn_test = "mardia", scale = TRUE, descriptives = TRUE, bootstrap = TRUE, B = 10000)
summary(data_mn3)
```

# Sample characteristics
Note that the values here are raw data after outlier removal.
```{r}
# Load the data again, as some variables were not included in normality and outlier detection steps.
data_des <- read_excel("/Users/chia-chuanyu/Desktop/dissertationData/study1/study1_organizedFinal.xlsx", sheet = "finalForAnalyze")
data_des <- data_des[-outliers, ]
catVars <- c("sex", "race", 'gender', 'ethnicity', 'selfDegree', 'marry', 'selfIncome', 'employment', 'past6monthAthleticCompetition', 'everAthleticCompetition')
CreateTableOne(data = data_des, vars = catVars, factorVars = catVars)

conVars <- c('age', 'ipaqsf_totalMET', 'eai', 'edeqs', 'phq_9', 'mossss_overallSupportIndex', 'srq', 'fomos', 'everyDiscrimiS')
describe(data_des[, conVars])

print("The # and % of people with EAI score ≥ 29 (the cutoff for high-risk by Szabo, A., Pinto, A., Griffiths, M. D., Kovacsik, R., & Demetrovics, Z. (2019). The psychometric evaluation of the Revised Exercise Addiction Inventory: Improved psychometric properties by changing item response rating. Journal of Behavioral Addictions, 8(1), 157-161.)")
print(sum(data_des$eai >= 29, na.rm = TRUE))
print((sum(data_des$eai >= 29, na.rm = TRUE)) / sum(!is.na(data_des$eai)))
```

# Simple Correlation for EA
No p-value adjestment becasue we are exploring the data.\
Spearman is used becasue the data violated multivariate normality.
```{r corr-plot, fig.width=10, fig.height=8}
# Specify vars again, since we don't use sex in correlation, which was used in outlier detection.
vars <- c('eai', 'edeqs', 'phq_9', 'mossss_overallSupportIndex', 'srq', 'fomos', 'everyDiscrimiS', 'ipaqsf_totalMET')
corr <- corr.test(
  data_clean[, c(vars)],
  use = "pairwise", method = "spearman", adjust = "none")
new_labels <- c("EA", "ED", "Depress", "SS", "SR", "FoMO", "Discrim", "PA")
rownames(corr$r) <- new_labels
colnames(corr$r) <- new_labels
rownames(corr$p) <- new_labels
colnames(corr$p) <- new_labels
corr$stars

p <- ggcorrplot.mixed(corr$r, upper = "ellipse", p.mat = corr$p, insig = "label_sig", sig.lvl = c(.05, .01, .001))
col1 <- colorRampPalette(c("#00007F", "blue", "#007FFF", "#FF7F00", "red", "#7F0000"))
p <- p + scale_fill_gradientn(colours = col1(10), limits = c(-1, 1),
  guide = guide_colorbar(direction = "horizontal", title = "", nbin = 1000,
  ticks.colour = "black", frame.colour = "black", barwidth = 15, barheight = 1.5)) +
  scale_colour_gradientn(colours = col1(10), limits = c(-1, 1),
  guide = guide_colorbar(direction = "horizontal", title = "", nbin = 1000,
  ticks.colour = "black", frame.colour = "black", barwidth = 15, barheight = 1.5)) +
  #ggtitle("Spearman Correlation between Variables") +
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5, size = 14, face = "bold"))
p
ggsave(filename = "correlation_plot.png", plot = p, width = 7, height = 7, dpi = 300)

# Our non-parametric correlation showed that EA is positively correlated with eating disorder, depression, social reward, fear of missing out, perceived discrimination, and physical activity.
```

# Partial Correlation for PA
```{r}
paVars <- c("eai", "mossss_overallSupportIndex", "srq", "fomos", "everyDiscrimiS")
covariates <- c("sex", "edeqs", "phq_9")

results <- data.frame("Social-PA Correlations when Controlling for Covariates" = paVars, Partial_r = NA, p_value = NA)

for (i in seq_along(paVars)) {
  df_subset <- data_clean[, c("ipaqsf_totalMET", paVars[i], covariates)]
  pcor_res <- pcor(df_subset, method = "spearman")
  results$Partial_r[i] <- pcor_res$estimate[1, 2]
  results$p_value[i] <- pcor_res$p.value[1, 2]
}
results
```

# Log transformation and scaling
```{r}
# data_clean <- data_clean %>%
#   mutate(
#     eai  = log(eai),
#     edeqs = log(edeqs + 1),
#     phq_9 = log(phq_9 + 1),
#     ipaqsf_totalMET = log(ipaqsf_totalMET + 1),
#     mossss_overallSupportIndex = log(mossss_overallSupportIndex),
#     srq  = log(srq),
#     fomos = log(fomos),
#     everyDiscrimiS = log(everyDiscrimiS + 1)
#   )
# data_clean$eai <- scale(data_clean$eai)
# data_clean$edeqs <- scale(data_clean$edeqs)
# data_clean$phq_9 <- scale(data_clean$phq_9)
# data_clean$ipaqsf_totalMET <- scale(data_clean$ipaqsf_totalMET)
# data_clean$mossss_overallSupportIndex <- scale(data_clean$mossss_overallSupportIndex)
# data_clean$srq <- scale(data_clean$srq)
# data_clean$fomos <- scale(data_clean$fomos)
# data_clean$everyDiscrimiS <- scale(data_clean$everyDiscrimiS)
```

# Hypothesis testing for social support (SS)
```{r}
model.ss <- lm(eai ~ mossss_overallSupportIndex + sex + ipaqsf_totalMET + phq_9 + edeqs +
                 mossss_overallSupportIndex*edeqs, data = data_clean)
summary(model.ss)
print(lm.beta::lm.beta(model.ss))
print(confint(model.ss))

p1 <- interact_plot(model.ss, pred = "mossss_overallSupportIndex", modx = "edeqs",
                    x.label = "Social Support", y.label = "EA Risk", interval = TRUE,
                    colors = c("#0072B2", "#E69F00", "#009E73")) +
                    theme_classic(base_size = 12) + theme(legend.position = "none")
p1
```

# Hypothesis testing for social reward (SR)
```{r}
model.sr <- lm(eai ~ srq + sex + ipaqsf_totalMET + phq_9 + edeqs + 
                   srq*edeqs, data = data_clean)
summary(model.sr)
print(lm.beta::lm.beta(model.sr))
print(confint(model.sr))
sim_slopes(model.sr, pred = srq, modx = edeqs)

p2 <- interact_plot(model.sr, pred = "srq", modx = "edeqs",
                    x.label = "Social Reward", y.label = "EA Risk", interval = TRUE, legend.main = "Eating Disorder Symptoms",
                    colors = c("#0072B2", "#E69F00", "#009E73")) +
                    theme_classic(base_size = 12)
p2
```

# Hypothesis testing for fear of missing out (fomos)
```{r}
model.fomos <- lm(eai ~ fomos + sex + ipaqsf_totalMET + phq_9 + edeqs + 
                   fomos*edeqs, data = data_clean)
summary(model.fomos)
print(lm.beta::lm.beta(model.fomos))
print(confint(model.fomos))
sim_slopes(model.fomos, pred = fomos, modx = edeqs)

p3 <- interact_plot(model.fomos, pred = "fomos", modx = "edeqs",
                    x.label = "Fear of Missing Out", y.label = "EA Risk", interval = TRUE,
                    colors = c("#0072B2", "#E69F00", "#009E73")) +
                    theme_classic(base_size = 12) + theme(legend.position = "none")
p3
```

# Hypothesis testing for discrimination (dis)
```{r}
model.dis <- lm(eai ~ everyDiscrimiS + sex + ipaqsf_totalMET + phq_9 + edeqs + 
                   everyDiscrimiS*edeqs, data = data_clean)
summary(model.dis)
print(lm.beta::lm.beta(model.dis))
print(confint(model.dis))
sim_slopes(model.dis, pred = everyDiscrimiS, modx = edeqs)

p4 <- interact_plot(model.dis, pred = "everyDiscrimiS", modx = "edeqs",
                    x.label = "Perceived Discrimination", y.label = "EA Risk", interval = TRUE,
                    colors = c("#0072B2", "#E69F00", "#009E73")) +
                    theme_classic(base_size = 12) + theme(legend.position = "none")
p4
```

# Combine all regression plots
```{r}
combined_plot <- (p1 | p2) / (p3 | p4) +plot_annotation(tag_levels = "a", tag_prefix = "(", tag_suffix = ")")
combined_plot
ggsave("interaction_plots.png", plot = combined_plot, width = 10,height = 7, units = "in", dpi = 300)
```

# FDR Correction
Since We have fours models, we need to apply FDR to control for inflated Type I error.
```{r}
p_values <- c(#summary(model.ss)$coefficients["mossss_overallSupportIndex", "Pr(>|t|)"],
              summary(model.ss)$coefficients["mossss_overallSupportIndex:edeqs", "Pr(>|t|)"],
              #summary(model.sr)$coefficients["srq", "Pr(>|t|)"],
              summary(model.sr)$coefficients["srq:edeqs", "Pr(>|t|)"],
              #summary(model.fomos)$coefficients["fomos", "Pr(>|t|)"],
              summary(model.fomos)$coefficients["fomos:edeqs", "Pr(>|t|)"],
              #summary(model.dis)$coefficients["everyDiscrimiS", "Pr(>|t|)"],
              summary(model.dis)$coefficients["everyDiscrimiS:edeqs", "Pr(>|t|)"])
adjusted_p_values <- p.adjust(p_values, method = "fdr")
# Below are the fdr-corrected p values for the interactions of SS*ED, SR*ED, FoMOS*ED, and Dis*ED
adjusted_p_values

print("mossss_overallSupportIndex:edeqs")
confint(emmeans(model.ss, ~ mossss_overallSupportIndex*edeqs), adjust = "fdr")
print("srq:edeqs")
confint(emmeans(model.sr, ~ srq*edeqs), adjust = "fdr")
print("fomos:edeqs")
confint(emmeans(model.fomos, ~ fomos*edeqs), adjust = "fdr")
print("everyDiscrimiS:edeqs")
confint(emmeans(model.dis, ~ everyDiscrimiS*edeqs), adjust = "fdr")
```

# Supplementary Analysis Examining the Relationships between PA and Social Interaction Dimensions
```{r}
print("PA-Social Support Relationship")
model.pa.ss <- lm(ipaqsf_totalMET ~ mossss_overallSupportIndex + sex + eai + phq_9 + edeqs +
                    mossss_overallSupportIndex*edeqs, data = data_clean)
summary(model.pa.ss)
print(lm.beta::lm.beta(model.pa.ss))
print(confint(model.pa.ss))

print("PA-Social Reward Relationship")
model.pa.sr <- lm(ipaqsf_totalMET ~ srq + sex + eai + phq_9 + edeqs + srq*edeqs, data = data_clean)
summary(model.pa.sr)
print(lm.beta::lm.beta(model.pa.sr))
print(confint(model.pa.sr))

print("PA-FoMO Relationship")
model.pa.fomos <- lm(ipaqsf_totalMET ~ fomos + sex + eai + phq_9 + edeqs + fomos*edeqs, data = data_clean)
summary(model.pa.fomos)
print(lm.beta::lm.beta(model.pa.fomos))
print(confint(model.pa.fomos))

print("PA-Discrimination Relationship")
model.pa.dis <- lm(ipaqsf_totalMET ~ everyDiscrimiS + sex + eai + phq_9 + edeqs + everyDiscrimiS*edeqs, data = data_clean)
summary(model.pa.dis)
print(lm.beta::lm.beta(model.pa.dis))
print(confint(model.pa.dis))
```

# Conclusion
* When covariates were considered, we found that EA was significantly correlated with greater FoMO and perceived discrimination only when eating disorder symptoms were high.
 - These ED-social interactions remained significant after FDR correction.
* When covariates were considered, we found that PA was not correlated with any dimension of social interaction.